### 2022-11-30 ms.rmd
Adding CVR models. Need to run VR too, but CVR for now

```{r acclimation_cap}
########################
### Differences in acclimation capacity between terrestrial, aquatic and marine
########################

#############
## lnRRQ10
#############
###################################
# Organise the data and prune tree
###################################
# Subset the data
lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))

@@

>>>>

```{r acclimation_cap}
#############
## lnRRQ10
#############
###################################
# Organise the data and prune tree
###################################
# Subset the data
lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))

@@

```{r}
#############
## lnCVRQ10
#############
  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))

# Check and prune tree
  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good

# Create the phylo correlation matrix
  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix

# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
  hist(lnCVRQ10_data$V)

# Studies with big V, why? Check N
  lnCVRQ10_data %>% filter(V >= 2)

##################################
# Model 2.1: Intercept only model.
# Used for heterogeneity analysis
##################################
rerun = TRUE
if(rerun){
  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data) 
  # Save model1.1
  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
} else{ model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")}
